---
title: "EIST Mapping 2022: Field Mapping of Knowledge Structure"
author: "Daniel S. Hain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    theme: flatly
    code_folding: hide
    df_print: paged
    number_sections: true
    toc: false
    toc_depth: 3
    toc_float:
      collapsed: false
params:
    institute: 
       value: null
    department:
       value: null
---

<!---
# Add to YAML when compiling html --< when reviewing change first line to: html_notebook
  html_document:
    theme: flatly
    code_folding: hide
    df_print: paged
    number_sections: true
    toc: false
    toc_depth: 3
    toc_float:
      collapsed: false

# Add when compiling pdf
# Add to YAML when compiling html
   bookdown::pdf_document2: 
    fig_caption: true
    number_sections: true
    global_numbering: true
--->


```{=html}
<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```

```{r setup, include=FALSE}
### Generic preamble
#rm(list=ls())
Sys.setenv(LANG = "en")
options(scipen = 5)
set.seed(1337)

### Load packages  
# general
library(tidyverse)
library(magrittr)
library(widyr)

# Kiblio & NW
library(bibliometrix)
library(tidygraph)
library(ggraph)

# NLP
library(tidytext)

# Dataviz
library(plotly)
library(ggforce)
library(ggrepel)
library(patchwork)

# Knit
library(knitr) # For display of the markdown
library(kableExtra) # For table styling

# own functions
source("../functions/functions_basic.R")
source("../functions/functions_summary.R")
source("../functions/00_parameters.R")

# Knitr options
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
```

<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

```{r, include=FALSE}
# When doing it here in the notebook
var_inst <- 'EIST'
var_dept <- 'v2'

# When calling from a highert level script
#var_inst <- params$institute
#var_dept <- params$department
```

# Introduction: Mapping of broad research field around `r var_inst` in `r var_dept`

Here are preliminary results of the bibliometric mapping of EIST. Its purpose is:

* To map the broader research community and distinct research field the department contributes to.
* Identify core knowledge bases, research areas gtrends and topics.
* Highlight the positioning of the department within this dynamics.

The method for the research-field-mapping can be reviewed here:

[Rakas, M., & Hain, D. S. (2019). The state of innovation system research: What happens beneath the surface?. Research Policy, 48(9), 103787.](https://doi.org/10.1016/j.respol.2019.04.011)

**Note:** The analysis in this document depicts the *larger research field* around the department, thereby all analysis results are based on the publications of the department plus related 


<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

```{r, include=FALSE}
# Load data
M <- readRDS(paste0('../../temp/M_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) %>% as_tibble() %>% 
  distinct(UT, .keep_all = TRUE) %>% 
  filter(PY >= PY_min, PY <= PY_max) %>%
  group_by(PY) %>%
    mutate(TC_cohort_rank = percent_rank(TC)) %>%
  ungroup() 
```

```{r}
com_labels <- read_csv2('../data/community_labeling.csv')  %>% filter(institute == var_inst, department == var_dept) %>% arrange(institute, department, type, com) %>% mutate(label = ifelse(is.na(label), paste0(type, ' ', com, ': unlabeled'), paste0(type, ' ', com, ': ', label)))
```
<!---
# Seed Articles

**Note:** The seed articles deemed representative for the active areas of research in the institution, and include authors affiliated with the institution. The departments research field is identified by selecting the 2000 most similar publications to the selected seed articles. See `Technical description`for additional explanations.

```{r, include=FALSE}
seed <-convert2df(file = paste0('../../data/seeds/scopus_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '_seed_select.csv'), dbsource = "scopus", format = "csv") %>%
  as_tibble() %>%
  mutate(seed = TRUE) 
```

```{r}
seed %>%
  select(AU, PY, TI, JI) %>%
  mutate(AU = AU %>% str_trunc(30),
         TI = TI %>% str_trunc(100),
         JI = JI %>% str_trunc(30)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 10)
```

--->

# General Overview over the research field

**Note:** This section provides basic descriptives of th identified research fielld, including number of articles over time, countries, institutions, and authors. See `Technical description`for additional explanations.

```{r, include=FALSE}
# results <- biblioAnalysis(M, sep = ";")
results <- read_rds(paste0('../../temp/M_res_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))
```

## Main Indicators: Publications, Authors, Countries 

```{r}
#results %>% plot(k = 10, pause = FALSE)
```

```{r}
prod_AU <- M %>% authorProdOverTime(k = 10, graph = TRUE)
#plot(prod_AU$graph)
```

```{r, include=FALSE}
rm(results, prod_AU)
```

## Connection between the research field's Top Authors-Keywords-Journals

```{r, include=FALSE}
M_threefield <- readRDS(paste0('../../temp/threefield_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) 
```

```{r, fig.width=17.5, fig.height=17.5}
M_threefield
```

# Topic modelling 

**Note:** Here, we report the results of a LDA topic-modelling (basically, clustering on words) on all title+abstract texts. Identified topics can be interpreted as broad themes in the research field. See `Technical description`for additional explanations.

```{r, include=FALSE}
text_tidy <- readRDS(paste0('../../temp/text_tidy_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))
text_lda <- readRDS(paste0('../../temp/text_LDA_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) 

text_lda_beta <- text_lda %>% tidy(matrix = "beta") 
text_lda_gamma <- text_lda %>% tidy(matrix = "gamma")
```

```{r, include=FALSE}
com_names_top <- tibble( 
  com = 1:(text_lda_gamma %>% pull(topic) %>% n_distinct()),
  type = 'TP',
  col = com %>% gg_color_select(pal = pal_tp)) %>%
  left_join(com_labels %>% filter(type == 'TP') %>% select(com, label), by = 'com') %>%
  mutate(label = ifelse(is.na(label), paste0('TP ', com, ': unlabeled'), label))
            
# # 1st alternative: Number them 1-n
# paste(type, 1:(text_lda_gamma %>% pull(topic) %>% n_distinct()))           
```

```{r, include=FALSE}
text_lda_beta %<>%  inner_join(com_names_top %>% select(com, label, col), by = c('topic' = 'com'))
text_lda_gamma %<>% inner_join(com_names_top %>% select(com, label, col), by = c('topic' = 'com'))
```


## Topics by topwords

```{r, fig.width=15, fig.height=15} 
text_lda_beta %>%
  group_by(label) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  mutate(term = reorder_within(term, beta, label)) %>%
  ggplot(aes(term, beta, fill = factor(label))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ label, scales = "free", ncol = 3) +
  coord_flip() +
  scale_x_reordered() +
  labs(x = "Intra-topic distribution of word",
       y = "Words in topic") + 
  scale_fill_manual(name = "Legend", values = com_names_top %>% pull(col)) +
  theme(legend.position = 'bottom')

#plot_ly <- plot %>% plotly::ggplotly()
#htmlwidgets::saveWidget(plotly::as_widget(plot_ly), '../output\vis_plotly_topic_terms.html', selfcontained = TRUE)
```

**Note:** While this static vies is helpful, I recommend using the interactive LDAVis version to be found under `r paste0('https://daniel-hain.github.io/biblio_lux_2022/output/topic_modelling/LDAviz_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '/index.html#topic=1&lambda=0.60&term=')`. For functionality and usage, see ´Technical ´.

```{r, fig.width = 15, fig.height=7.5}
text_lda_gamma %>%
  rename(weight = gamma) %>%
  left_join(M %>% select(XX, PY), by = c('document' = 'XX')) %>%
  mutate(PY = as.numeric(PY)) %>%
  group_by(PY, label) %>% summarise(weight = sum(weight)) %>% ungroup() %>%
  group_by(PY) %>% mutate(weight_PY = sum(weight)) %>% ungroup() %>%
  mutate(weight_rel = weight / weight_PY) %>%
  select(PY, label, weight, weight_rel) %>%
  filter(PY >= PY_min & PY <= PY_max) %>%
  arrange(PY, label) %>%
  plot_summary_timeline(y1 = weight, y2 = weight_rel, t = PY, t_min = PY_min, t_max = PY_max, by = label,  label = TRUE, pal = pal_tp, 
                        y1_text = "Topic popularity annualy", y2_text = "Share of topic annually") +
  plot_annotation(title = paste('Topic Modelling:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  caption = 'Absolute topic appearance (left), Relative topic appearance (right)')
```

```{r, fig.width = 15, fig.height=7.5}
text_lda_gamma %>%
  rename(weight = gamma) %>%
  inner_join(M %>% select(XX, PY, TC_cohort_rank) %>%
              filter(int_dept = TRUE), by = c('document' = 'XX')) %>%
  # mutate(impact = weight* TC_cohort_rank) %>%
  mutate(impact = TC_cohort_rank >= 0.9) %>%
  group_by(PY) %>%
  filter(percent_rank(weight) >= 0.5) %>%
  ungroup() %>%
  group_by(label, PY) %>%
  summarise(impact = mean(impact)) %>%
  ggplot(aes(x = PY, y = impact, col = label)) +
  geom_line() + 
  geom_point() + 
  theme(legend.position = 'bottom') +
  labs(title = paste('Topic Impact:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  x = 'Year',
                  y = 'Topic Impact',
                  caption = 'Topic Impact refers to the share of publications within the cohort top-10% cited publications associated with the topic',
                  )
```

<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->


```{r, include=FALSE}
rm(text_tidy, text_lda)
```

# Knowledge Bases: Co-Citation network analysis 

**Note:** This analysis refers the co-citation analysis, where the cited references and not the original publications are the unit of analysis. Identified knowledge bases can be interpreted as the knowledge foundation the field draws from. See `Technical description`for additional explanations.

```{r, include=FALSE}
C_nw <- readRDS(paste0('../../temp/C_nw_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))  %>%
  drop_na(com)
```

```{r, include=FALSE}
com_names_cit <- tibble( 
  com = 1:(C_nw %>% pull(com) %>% n_distinct()),
  type = 'KB',
  col = com %>% gg_color_select(pal = pal_kb)) %>%
  left_join(com_labels %>% filter(type == 'KB') %>% select(com, label), by = 'com') %>%
  mutate(label = ifelse(is.na(label), paste0('KB ', com, ': unlabeled'), label))

# # 1st alternative: Number them 1-n
# paste(type, 1:(C_nw %>% pull(com) %>% n_distinct()))
```

```{r, include=FALSE}
C_nw %<>% left_join(com_names_cit %>% select(com, label, col), by = "com")
```

```{r, include=FALSE}
kb_stats <- C_nw %>%
  group_by(label) %>%
  summarise(n = n(), density_int = ((sum(dgr_int) / (n() * (n() - 1))) * 100) %>% round(3)) %>%
  relocate(label, everything())
```

```{r}
kb_sum <-C_nw %>% group_by(com) %>% 
  arrange(com, desc(dgr_int)) %>%
  mutate(name = name %>% str_trunc(150)) %>%
  slice_max(order_by = dgr_int, n = 10, with_ties = FALSE) %>% 
  ungroup() %>%
  select( name, dgr_int, dgr) %>%
  kable() 

for(i in 1:nrow(com_names_cit)){
  kb_sum <- kb_sum %>%
    pack_rows(paste0('Knowledge Base ', i, ': ', com_names_cit[i, 'label'],
                     '   (n = ', kb_stats[i, 'n'], ', density =', kb_stats[i, 'density_int'] %>% round(2), ')' ), 
              (i*10-9),  (i*10), label_row_css = "background-color: #666; color: #fff;") 
  }

kb_sum %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 10)
```

```{r, include=FALSE}
el_2m <- readRDS(paste0('../../temp/el_2m_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) %>%
  drop_na()
```


```{r, include=FALSE}
cit_com_year <- el_2m %>%
  count(com_cit, PY, name = 'TC') %>%
  group_by(PY) %>%
  mutate(TC_rel = TC / sum(TC)) %>%
  ungroup() %>%
  arrange(PY, com_cit) %>%
  left_join(com_names_cit , by = c('com_cit' = 'com')) %>% 
  complete(label, PY, fill = list(TC = 0, TC_rel = 0))
```

```{r, fig.width = 15, fig.height=7.5}
cit_com_year %>%
  plot_summary_timeline(y1 = TC, y2 = TC_rel, t = PY, t_min = PY_min, t_max = PY_max, by = label, pal = pal_kb, label = TRUE,
                        y1_text = "Number citations recieved annually",  y2_text = "Share of citations recieved annually") +
  plot_annotation(title = paste('Knowledge Bses:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  caption = 'Absolute knowledge base appearance (left), Relative knowledge base appearance (right)')
```

<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

# Research Areas: Bibliographic coupling analysis

**Note:** This analysis refers the bibliographic coupling analysis, where original publications are the unit of analysis. Identified research areas can be interpreted as the field's current research frontier. See `Technical description`for additional explanations.

```{r, include=FALSE}
M_bib <- readRDS(paste0('../../temp/M_bib_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) %>% 
  as_tibble() %>%
  drop_na(com)
```

```{r, include=FALSE}
com_names_bib <- tibble( 
  com = 1:(M_bib %>% pull(com) %>% n_distinct()),
  type = 'RA',
  col = com %>% gg_color_select(pal = pal_ra)) %>%
  left_join(com_labels %>% filter(type == 'RA') %>% select(com, label), by = 'com') %>%
  mutate(label = ifelse(is.na(label), paste0('RA ', com, ': unlabeled'), label))

# # 1st alternative: Number them 1-n
# paste(type, 1:(M_bib %>% pull(com) %>% n_distinct()))
```

```{r, include=FALSE}
M_bib %<>% left_join(com_names_bib %>% select(com, label, col), by = "com")
```

```{r, include=FALSE}
ra_stats <- M_bib %>%
  drop_na(com) %>%
  group_by(com, label) %>%
  summarise(n = n(), density_int = ((sum(dgr_int) / (n() * (n() - 1))) * 100) %>% round(3)) %>%
  select(com, label, everything())
```

```{r}
ra_sum <- M_bib %>% group_by(label) %>% 
  left_join(M %>% select(XX, AU, PY, TI, TC), by = 'XX') %>%
  mutate(dgr_select = (dgr_int / max(dgr_int) * (TC / max(TC))) ) %>%
  slice_max(order_by = dgr_select, n = 10, with_ties = FALSE) %>% 
  mutate(TC_year = (TC / (2021 + 1 - PY)) %>% round(2),
         dgr_int = dgr_int %>% round(2),
         AU = AU %>% str_trunc(25),
         TI = TI %>% str_trunc(125)) %>%
  ungroup() %>%
  select(AU, PY, TI, dgr_int, TC, TC_year) %>%
  kable()


for(i in 1:nrow(com_names_bib)){
  ra_sum  %<>%
    pack_rows(paste0('Research Area ', i, ': ', com_names_bib[i, 'label'],
                     '   (n = ', ra_stats[i, 'n'], ', density =', ra_stats[i, 'density_int'] %>% round(2), ')' ), 
              (i*10-9),  (i*10), label_row_css = "background-color: #666; color: #fff;") 
  }

ra_sum %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 10)
```

```{r, fig.width = 15, fig.height=7.5}
M_bib %>%
  left_join(M %>% select(XX, PY), by = 'XX') %>%
  mutate(PY = PY %>% as.numeric()) %>%
  group_by(label, PY) %>% summarise(n = n()) %>% ungroup() %>%
  group_by(PY) %>% mutate(n_PY = sum(n)) %>% ungroup() %>%
  mutate(n_rel = n / n_PY) %>%
  select(label, PY, n, n_rel) %>%
  arrange(label, PY) %>% 
  complete(label, PY, fill = list(n = 0, n_rel = 0)) %>%
  plot_summary_timeline(y1 = n, y2 = n_rel, t = PY, t_min = PY_min, t_max = PY_max, by = label, label = TRUE, pal = pal_ra,
                        y1_text = "Number publications annually", y2_text = "Share of publications annually") +
  plot_annotation(title = paste('Research Areas:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  caption = 'Absolute research area appearance (left), Relative research area appearance (right)')
```


```{r, include=FALSE}
g_agg <- readRDS(paste0('../../temp/g_bib_agg_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) %N>%
  arrange(com) # %>%
#   mutate(name = names_ra %>% pull(com_ra_name),
#          color = cols_ra)
```

```{r, fig.height= 7.5, fig.width=7.5}
g_agg %E>% 
  filter(weight > 0 & from != to) %>%
  filter(weight >= quantile(weight, 0.25) )  %N>%
  mutate(com = com_names_bib %>% pull(label)) %>%
  ggraph(layout = "circle") + 
  geom_edge_fan(strenght = 0.8, aes(width = weight), alpha = 0.2)  + 
  geom_node_point(aes(size = N, color = com))  + 
  geom_node_text(aes(label = com), repel = TRUE) +
  #theme_graph(base_family = "Arial") +
  theme(legend.position = 'bottom') +
  scale_size(range = c(2,20)) +
  scale_color_brewer(palette = pal_ra) +
  labs(title = paste('Research Area Connectivity:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  caption = 'Nodes = Identified Research Areas; Edges: Bibliographic coupling strenght (Jaccard weighted)')
```


# Knowledge Bases, Research Areas & Topics Interaction

```{r, include=FALSE}
# Nodes
nl_3m <- com_names_bib %>%
  bind_rows(com_names_cit) %>%
  bind_rows(com_names_top) %>%
  rename(name = label,
         com_nr = com) %>%
  relocate(name)

# Edges
el_2m_kb <- el_2m %>%
  select(-from, -to) %>%
  inner_join(com_names_cit %>% select(com, label), by = c('com_cit' = 'com')) %>%
  inner_join(com_names_bib %>% select(com, label, col), by = c('com_bib' = 'com')) %>%
  mutate(weight = 1) %>%
  rename(from = label.x,
         to = label.y) %>% # generic
  select(from, to, weight, col) %>% 
  drop_na() %>% 
  count(from, to, col, wt = weight, name = 'weight') %>%
  filter(percent_rank(weight) >= 0.25) %>%
  weight_jaccard(i = from, j = to, w = weight) %>% 
  select(-weight)

el_2m_topic <- text_lda_gamma %>% select(-topic, -col) %>%
  left_join(M_bib %>% select(XX, com) %>% drop_na(com), by = c('document' = 'XX')) %>%
  inner_join(com_names_bib %>% select(com, label, col), by = c('com' = 'com')) %>%
  rename(from = label.y,
         to = label.x,
         weight = gamma) %>% # generic
  select(from, to, weight, col) %>% 
  drop_na() %>% 
  count(from, to, col, wt = weight, name = 'weight') %>%
  filter(percent_rank(weight) >= 0.25) %>%
  weight_jaccard(i = from, j = to, w = weight) %>% select(-weight)

# graph
g_3m <- el_2m_kb %>% 
  bind_rows(el_2m_topic) %>%
  as_tbl_graph(directed = TRUE) %N>%
  left_join(nl_3m, by = 'name') %>%
  mutate(
    level = case_when(
      type == "KB" ~ 1,
      type == "RA" ~ 2,
      type == "TP" ~ 3),
    coord_y = 0.1,
    coord_x = 0.001 + 1/(max(level)-1) * (level-1)
    )  %N>%
  filter(!is.na(level))
```

```{r, include=FALSE}
## Build sankey plot
fig <- plot_ly(type = "sankey", 
               orientation = "h",
               arrangement = "snap",
  node = list(
    label = g_3m %N>% as_tibble() %>% pull(name),
    x = g_3m %N>% as_tibble() %>% pull(coord_x),
    y = g_3m %N>% as_tibble() %>% pull(coord_y),
    color = g_3m %N>% as_tibble() %>% pull(col), 
    pad = 4
  ), 
  link = list(
    source = (g_3m %E>% as_tibble() %>% pull(from)) -1,
    target = (g_3m %E>% as_tibble() %>% pull(to)) -1,
    value =  g_3m %E>% as_tibble() %>% pull(weight_jac),
    color = g_3m %E>% as_tibble() %>% pull(col) %>% col2rgb() %>% as.matrix() %>% t() %>% as_tibble() %>% 
      mutate(col_rgb = paste0('rgba(', red, ',' , green, ',', blue, ',0.75)')) %>%  pull(col_rgb)
    )
) %>% 
  layout(title = paste('Knowledge Bases, Research Areas & Topics:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
         margin = list(l = 50, r = 50, b = 100, t = 100, pad = 2)) 
```


## Joint Overview over Knowledge Bases, Research Areas, and Topics

This plot shows the connection of publications in the research areas to knowledge bases (by citations) and topics (by gamma, document-topic weight)

```{r, fig.height= 10, fig.width=15}
fig
```



# Trends 

```{r}
uni_sim <- read_rds(paste0('../../temp/uni_sim_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))
```

## Lead-Lag Analysis 

```{r, fig.height=5, fig.width=7.5}
desc <- uni_sim %>% 
  filter(AU_UN == paste(var_inst, var_dept)) %>%
  mutate(desc = paste0('N: ', n, ' \n',
                       'Similarity to past:', sim_past %>% round(2), ' \n',
                       'Similarity to future: ', sim_future %>% round(2), ' \n',
                       'Lead-Lag Score: ', future_trend %>% round(2))) %>% pull(desc)
  
  
uni_sim %>%
  slice_max(order_by = n, n = 100) %>%
  ggplot(aes(x = sim_past, y = sim_future)) +
  geom_mark_ellipse(aes(filter = AU_UN == paste(var_inst, var_dept), label = AU_UN, fill = 'red1'), description = desc) + guides(fill = FALSE) +
  #geom_point(data = uni_sim %>% filter(AU_UN == paste(var_inst, var_dept)), 
  #           aes(size = n), col = 'darkred') + 
  geom_point(aes(size = n, col = future_trend), alpha = 0.5) +
  geom_text_repel( 
    data =uni_sim %>% slice_max(order_by = n, n = 5) %>% filter(AU_UN != paste(var_inst, var_dept)), # Filter data first
    aes(label = AU_UN),
    box.padding = 1, max.overlaps = Inf) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", col = 'snow3') +
  scale_colour_gradient(low = "blue", high = "red", name = "Lead-Lag Score") +
  theme(legend.position = 'bottom') +
  labs(x = 'Similarity to past',
       y = 'Similarity to future',
       title = paste('Field Lead-Lag Analysis:', var_inst, var_dept, sep = ' '),
       subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
       caption = 'x and y axis')
# + lims(x = c(0.625, 0.725), y = c(0.625, 0.725))
```

<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

# Collaboration 

```{r}
el_inst <- readRDS(paste0('../../temp/el_inst_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))
```


```{r}
g_inst <- el_inst %>% as_tbl_graph(directed = FALSE) %E>%
  filter(weight >= cutof_edge_cit ) %N>%
  filter(!node_is_isolated())
```

## Collaboration network 

```{r, fig.height= 10, fig.width=15}
g_inst %N>% 
  mutate(cent = centrality_degree(weights = weight)) %>%
  filter(name == paste(var_inst, var_dept)  | rank(-cent) <= 100 ) %>%
  ggraph(layout = "fr") + 
  geom_edge_link(aes(width = weight,
                     #color = .N()$name[from] == paste(var_inst, var_dept) | .N()$name[from] == paste(var_inst, var_dept),
                     filter = (weight >= weight  %>% quantile(0.25)))
                 , alpha = 0.25)  + 
  geom_node_point(aes(size = cent), col = 'steelblue1')  + 
  geom_node_text(aes(label = name, 
                     size = cent,
                     filter = (cent >= cent  %>% quantile(0.8))), repel = TRUE) +
  #theme_graph(base_family = "Arial") +
  theme(legend.position = 'bottom') +
  scale_edge_width_continuous(range = c(0.5, 5))  +
  scale_edge_colour_manual(values = c("grey", "red"), name = '1st degree') +
  scale_size(range = c(0.5,10)) 
```

# Endnotes

```{r}
sessionInfo()
```

